Making Sequential Programs Deterministic

### 2019-04-03 experiment_tables.tex
deflaker expts

>>>>

\begin{table}[]
    \begin{tabular}{|l|p{5cm}|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664&test (added to test cases in det checker) \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker (Race condition issue) \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  Removed tests (Printing (HTTP's) Response.getstatus()) has Chinese characters,
        compilation with det checker stuck!\\ \hline
        togglz [19] issue \#223 & build issue \\ \hline
        togglz [20] issue \#240 &  build issue\\ \hline
    \end{tabular}
\end{table}

### 2019-04-03 experiments.tex
deflaker expts

\section{Comparison to previous work}

@@

\section{deflaker case study}
\begin{table}[]
    \begin{tabular}{|l|p{5cm}|}
        \hline
        Benchmark, issue & found by det checker? \\ \hline
        achilles, [2] issue \#309 &  Race condition\\ \hline
        achilles, [3] issue \#310 & Same fix for \#309 and \#310 \\ \hline
        checkstyle [4] issue \#4664&test (added to test cases in det checker) \\ \hline
        jackrabbit-oak [6] \#6512&  Unresolved on issue tracker (Race condition issue) \\ \hline
        jackrabbit-oak [7] issue \#6524&  Dead link, didn't find 6524 in issue tracker \\ \hline
        nutz [10] issue \#1283 &  Removed tests (Printing (HTTP's) Response.getstatus()) has Chinese characters,
        compilation with det checker stuck!\\ \hline
        togglz [19] issue \#223 & build issue \\ \hline
        togglz [20] issue \#240 &  build issue\\ \hline
    \end{tabular}
\end{table}

>>>>

\section{Comparison to NonDex}

@@

\section{Comparison to Deflaker}
Deflaker~\cite{deflaker}, like NonDex, reports tests that could be flaky. Ideally, we would have 
liked to run all three tools (NonDex, DeFlaker, and \TheDeterminismChecker) on an open source project
that wasn't explored by any of the tool for a fair comparison. Unfortunately, there are issues with the
DeFlaker plugin and we weren't able to run it on any project. We have created a Github issue for the same
in its repository.

\subsection{\TheDeterminismChecker on DeFlaker benchmarks}\label{sec:deflaker-benchmarks}
DeFlaker found 87 previously unknown flaky tests in 93 projects that were being actively developed at the the time
the paper was written. The authors reported 19 of these tests, out of which 7 were addressed by the maintainers of
those projects. Since we can only verify if \TheDeterminismChecker finds the same bugs by looking at the source code
locations, we ran our tool on the benchmarks where the reported bug was fixed. We again defer the reader to~\cite{deflaker}
for a complete list of the open source projects and their details.

Two of the seven flaky tests (in \<achilles> and \<jackrabbit-oak>) that DeFlaker reported were caused by a race condition. \TheDeterminismChecker
is designed for sequential programs and hence cannot detect this category of bugs.  
We couldn't find the link to one of the issues in the issue tracker of \<jackrabbit-oak>
We ran into build issues
for \<tigglz> and \<nutz> which had two and one flakiness issues respectively. 
\TheDeterminismChecker was able to find the source of flakiness in \<checkstyle>. This bug was in a test
case that deterministically accessed an \<OrderNonDet> array returned by \<Class.getDeclaredConstructors()>.
